Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-17 stp/paper_aaai/main.tex
Added stuff about unknown nodes
Related work for paper aaai, soccer experiments

@@

%  \pdfinfo{
%/Title (2018 Formatting Instructions for Authors Using LaTeX)
%/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Using Machine Learning and Constraint Programming to Solve the 
Relational-To-Ontology Mapping Problem}
\author{}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources in an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modelling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

@@

\section{Previous Work \label{SEC:pw}}
\ddg{rewrite, add more}
One of the standard approaches to solve the relational-to-ontology (\relonto{})
mapping problem is to apply Knowledge Representation and Reasoning (KR)
techniques. The main idea of this approach is to exploit constraints specified 
within relational schemata and ontologies. Several mapping generation
tools based on this approach already exist, for example, BootOX, MIRROR,
COMA++ \cite{pinkel2016rodi}. The issue is though that constraints may be 
inconsistent or absent completely \ddg{Why?}. We suggest to use ML techniques 
to overcome this hurdle.

\cite{taheriyan2016learning} \ddg{Isn't this really similar??}

@@

An ontology $\mathcal{O}$ is a specification of classes of objects, their 
data properties and relationships between them. An example of an ontology is 
given 
in Fig. \ref{FIG:onto}. A Class in an ontology can have \emph{data properties} 
or 
\emph{class properties}. For example an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). Also, a Class can be a subclass of another Class. For 
example ``Cities'' and ``States'' are both ``Places''. A subclass 
inherits all the properties of the parent class.

@@

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and 
an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. We
use the term ``appropriate'' since there might be many such triples which are
well-formed source descriptions, but only one or a few will capture the intended
meaning of the source. Our goal is to automatically build $\delta^\star$ such 
that it minimizes the \emph{graph edit distance} (GED) from the semantic model 
$m^\star$ to the semantic model $m^\dag$ that the user considers correct.

The GED is a measure of similarity between two graphs defined as follows for 
two graphs $g_1$ and $g_2$: $GED(g_1,g_2) = min_{(e_1 ,...,e_k)\in P} 
\sum_{i=1}^{k}c(e_i)$ where $P$ denotes the set of edit paths transforming 
$g_1$ into (a graph
isomorphic to) $g_2$ and $c(e) \geq 0$ is the cost of each graph edit operation 
$e$. Graph edit operations include among others node insertion, edge deletion, 
etc. \cite{gao2010survey}. In practice, we use some approximation measures of 
the graph edit distance. \ddg{which approx?}

@@

\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
confidence? If so, 
what is $k$?}

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ in 
such a way that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology. As we will see int he next section, this 
makes edges present in semantic models more attractive. \ddg{How exactly are 
they weighted?}

@@

\subsection{Frequent Subgraph Pattern Mining \label{SSEC:pattern-mining}}

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining
\cite{petermann2017dimspan,yan2002gspan}. We chose to use DIMSpan 
\cite{petermann2017dimspan}. \ddg{CHECK! How do they solve an NP-complete 
problem??}

This tool provides us with a list of patterns that are frequent, as well as 
their support. The \emph{support} of a pattern is a measure of frequency. Thus 
the higher the support, the more often the pattern appears. This typically 
means that big patterns have low support.

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham2016} or HTML 
tables \cite{ritze2017matching}.

@@

@@

\section{Conclusions}
\ddg{TODO}

\bibliographystyle{aaai}
\bibliography{main}
\end{document}

>>>>

% natalia
\usepackage{multirow}

@@

%  \pdfinfo{
%/Title (2018 Formatting Instructions for Authors Using LaTeX)
%/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources in an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modelling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

@@

@@

An ontology $\mathcal{O}$ is a specification of classes of objects, their 
data properties and relationships between them.
An example of an ontology is given in Fig. \ref{FIG:onto}. 
A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
For example an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). 
Also, a Class can be a subclass of another Class. 
For 
example ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.

@@

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and 
an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. We
use the term ``appropriate'' since there might be many such triples which are
well-formed source descriptions, but only one or a few will capture the intended
meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} from the semantic model 
$m^\star$ to the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

@@

\ddg{IMPORTANT: Do we keep all of them, or only the top $k$ with most 
confidence? If so, 
what is $k$?}
\npr{We keep all, that is the crucial difference from Karma which does some voodoo heuristic filtering}

@@

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ in 
such a way that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
As we will see in the next section, this makes edges present in semantic models more attractive. \ddg{How exactly are 
they weighted?}

@@

\subsection{Frequent Graph Pattern Mining \label{SSEC:pattern-mining}}

@@

Our goal is to take a set of graphs (the semantic models from the training set 
$S_T$) and find patterns that appear often across that set of graphs. This is 
known as the Frequent Subgraph Mining (FSM), which contains the subgraph 
isomorphism, known to be NP-complete. 
There exists a range of tools that can achieve this task using Transactional 
Frequent Graph Pattern Mining\cite{petermann2017dimspan,yan2002gspan}. 
We chose to use DIMSpan \cite{petermann2017dimspan}. 
\ddg{CHECK! How do they solve an NP-complete problem??}
\npr{Im not sure what to say here: there is just no guarantee how long it will take for the whole thing to run, except there is a threshold on how frequent they have to be; they use gSpan procedure to prune patterns and a variant of Ulmans algorithm for graph pattern matching}

This tool provides us with a list of patterns that are frequent, as well as 
their support. 
The \emph{support} of a pattern is a measure of frequency. 
Thus, the higher the support, the more often the pattern appears. This typically means that big patterns have low support.

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a reprocess that requires extra time and effort as this is typically done manually in the real world.

@@

We run experiments on two domains: museum and soccer (see Fig.~\ref{tab:data} for statistics).

\begin{table}[ht]\small
  \centering
  \caption{Description of data sources.}\label{tab:data}
		\begin{tabular}{ccccc} 
		\hline
		\multirow{2}{*}{\textbf{Domain}} & \# data & \# semantic & \# & \# unknown\\
		 & sources & labels & attributes & attributes\\
		\hline
		museum & 29 & 20 & 443 & 159  \\
		soccer & 12 & 18 & 138 & 42 \\
		\hline
		\end{tabular} 
\end{table}

%\begin{table*}[ht]
%  \centering
%  \caption{Description of data sources.}\label{tab:data}
%		\begin{tabular}{ccccccc} 
%		\hline
%		\multirow{2}{*}{\textbf{Domain}} & \# & \# semantic & \# & \# unknown & avg \# rows & avg \# attributes\\
%		 & sources & labels & attributes & attributes & per source & per source\\
%		\hline
%		museum & 29 & 20 & 443 & 159 & 6978.89 & 15.27 \\
%		soccer & 12 & 18 & 138 & 42 & 2120.16 & 11.5 \\
%		\hline
%		\end{tabular} 
%\end{table*}

@@

\begin{table}[t]\small
  \centering
  \caption{Average performance of semantic labeling for leave one out strategy.}
  	\label{tab:unknownloo}
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

\section{Related Work \label{SEC:pw}}
\ddg{rewrite, add more}

Relational data sources are still one of the most popular ways to store enterprise or Web data, however, the issue with relational schema is the lack of a well-defined semantic description.
A common ontology provides a way to represent the meaning of a relational schema and can facilitate the integration of heterogeneous data sources within a domain.
Indicating semantic correspondences manually might be appropriate if only few data sources need to be integrated, however, it becomes tedious with the growing number of heterogeneous schemata.
Hence, automatic or semi-automatic approaches for relational-to-ontology schema mapping are being actively developed.

The majority of approaches to solve the relational-to-ontology (\relonto{}) mapping problem are based on heuristic rules and alignment of constraints specified within relational schemata and ontologies.
A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
Further, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is the ability to run in a fully automatic setting.
Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
This opens an interesting direction for further research to develop an automatic system.

A major issue with fully automatic systems is though that constraints may be inconsistent or absent completely, e.g., tables on the Web \ddg{Why?}.
To overcome this issue, we can apply ML techniques.
\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
\cite{Limaye:Annotating} enrich their data sources by using YAGO.
\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
%extract additional data from knowledge bases to assign a semantic label to an attribute.
Hence, these approaches are limited to domains well represented in those knowledge bases.
Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
However, it might be further bootstrapped by leveraging external knowledge bases.
This is especially beneficial at the start when the system does not have sufficient training data.

As mentioned above, the approaches for mapping Web tables also perform semantic labeling.
They design various similarity metrics for attribute names and attribute values.
However, they disregard the attributes which are not matched to the ontology (the so-called \emph{unknown} class of attributes).
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
That is why we have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.

We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
These nodes serve to capture the unmatched attributes from the source.
Though we have modified Karma to treat these additional nodes as well, our approach outperforms Karma since we have additional constraints for these nodes and use an exact algorithm to solve the STP.
\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.

In their follow up work, \cite{Taheriyan:Leveraging} suggest to use graph patterns to boost the performance of their system.
To perform semantic modeling in such scenario, \cite{Taheriyan:Leveraging} had to revise their algorithm by introducing additional heuristics.
However, in our case we had to add pattern variables and to modify the objective function in the MiniZinc model.
No changes to the solver were required.
This makes our system very convenient and opens directions for validating various additional constraints.
Though our approach beats the state-of-the-art system Karma in the conducted experiments, it is worth noting that the scalability of our approach is under question.
The main argument why exact solution for STP is feasible in our setting is that we map data sources to a domain-specific ontology which is expected to be limited in its size.

\ddg{Isn't this really similar??}
\npr{It is very similar, I'm even using their code partially :)}

\section{Conclusion}
\ddg{TODO} 
In this paper we have introduced a new approach to solve the problem of relational-to-ontology schema mapping.

Future directions:
incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
incorporate schema and ontology constraints.

\bibliographystyle{aaai}
\npr{shorten citations}
\bibliography{main}
\end{document}
